Shift-sensitive Power Transformations for Transforming Data to Normality

### 2023-04-05 manuscript/manuscript.Rmd
WIP on multi-modal distribution plot.

-   We define an empirical measure of the goodness of fit for detecting cases when power transformations fail to yield a normally distributed transformed feature.

@@

```
We then consider the empirical probability of type I errors: the probability of incorrectly classifying a centrally normal distribution as being non-normal based on the test statistic. Under the assumption that the asymmetric generalised normal distributions are centrally normal after robust transformation, this produces the relationship shown in Figure *Insert*. Since for $\kappa \leq 0.80$ error curves are similar, we fix the value of the central portion $\kappa$ to 0.80. This leads to test statistic values listed in Table *insert*, which derive from the type I error rates of the Box-Cox transformation.

```{r goodness-of-fit-2, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Rejected transformed asymmetric generalised normal distributions as function of ",
  "the mean absolute residual error of the central portion $\\kappa$ of the distribution.")

@@

```{r include = FALSE, eval = FALSE}
table_data <- .get_test_statistics_data(manuscript_dir = manuscript_dir)
```

```{r include = FALSE, eval = FALSE}
load(file = "./R/sysdata.rda")

gof_lookup_table <- .get_test_statistics_data(manuscript_dir = manuscript_dir, reduce = TRUE, as_table = FALSE)
gof_lookup_table[, "method" := NULL]

usethis::use_data(
  gof_lookup_table, 
  two_sided_function_parameters, 
  internal = TRUE, 
  overwrite = TRUE)
```

@@

>>>>

-   We define an empirical goodness of fit test for detecting cases where power transformations fail to yield a normally distributed transformed feature.

@@

```
We then consider the empirical probability of type I errors: the probability of incorrectly classifying a centrally normal distribution as being non-normal based on the test statistic. Under the assumption that the asymmetric generalised normal distributions are centrally normal after robust transformation, this produces the relationship shown in Figure *Insert*. Since for $\kappa \leq 0.80$ error curves are similar, we fix the value of the central portion $\kappa$ to 0.80. This leads to test statistic values listed in Table *insert*, which derive from the type I error rates of the Yeo-Johnson transformation.

```{r goodness-of-fit-2, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Type 1 error rate of transformed asymmetric generalised normal distributions as function of ",
  "the test statistic for the central portion $\\kappa$ of the distribution.")

@@

```{r include = FALSE, eval = FALSE}
# This writes the lookup table for the goodness of fit test to the
# power.transform package.
load(file = "./R/sysdata.rda")

gof_lookup_table <- .get_test_statistics_data(
  manuscript_dir = manuscript_dir,
  reduce = TRUE,
  as_table = FALSE)
gof_lookup_table[, "method" := NULL]

usethis::use_data(
  gof_lookup_table, 
  two_sided_function_parameters, 
  internal = TRUE, 
  overwrite = TRUE)
```
```{r include = FALSE, eval = FALSE}
# This generates the data for the table below.
table_data <- .get_test_statistics_data(manuscript_dir = manuscript_dir)
```

@@

Figure *insert* shows bi-modal distributions, and their respective p-values using the empirical goodness of fit test.

```{r goodness-of-fit-3, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0("Bi-modal distributions and empirical goodness of fit test results.")

.plot_bimodal_distribution_test(
  plot_theme = plot_theme,
  manuscript_dir = manuscript_dir)
